\thetitle

### 2021-05-27 writing/discussion.tex
9.2 grammar / wording

The validity of these conclusions is threatened in two distinct ways. The first
set of threats concerns aspects of the experimental setup discussed in preceding
sections: (i) the representativity of benchmarks; (ii) the relation between the
mutations and real programming mistakes; and (iii) the sampling strategy.
Although the experimental setup attempts to mitigate against these threats, the
reader must definitely keep these limitations in mind when drawing conclusions.

The second set of threats questions four rather different aspects. To start
with, the realism of the rational programmer itself is questionable
(sec.~\ref{sub:rational}) as is the definition of ``interesting scenarios''
(sec.~\ref{sec:threat:erasure-bias}).  The remaining threats are about the
accuracy and cost of Transient blame, respectively
(secs.~\ref{sec:threat:transient} and~\ref{sec:threat:transient2}).

>>>>

The validity of these conclusions is threatened in two distinct ways. The first
set of threats concerns aspects of the experimental setup discussed in preceding
sections: (i) the representativeness of the benchmarks; (ii) the relation between the
mutations and real programming mistakes; and (iii) the sampling strategy.
Although the experimental setup attempts to mitigate these threats, the
reader must keep these limitations in mind when drawing conclusions.

The second set of threats questions four rather different aspects. To start
with, the realism of the rational programmer itself is questionable
(sec.~\ref{sub:rational}), as is the definition of ``interesting scenarios''
(sec.~\ref{sec:threat:erasure-bias}).  The remaining threats are about the
accuracy and cost of Transient blame, respectively
(secs.~\ref{sec:threat:transient} and~\ref{sec:threat:transient2}).
